Supplement to Automatic Matching of Bullet Lands

### 2016-01-06 imaging-supplement.Rnw
first attempt at labelling the aligned signatures.

\newpage
\section{Signature intensities}\label{supp:bulletbottom}
<<setup-signatures, echo=FALSE>>=
library(x3pr)
library(x3prplus)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(zoo)

@@

aligned <- crossSmooth %>% group_by(id) %>% do(
  data.frame(alignme(.))
)
aligned$land <- (aligned$id %% 6)
aligned$land[aligned$land==0] <- 6
qplot(x=y, y=l30, data=aligned, geom="line", group=bullet) + ylim(c(-7,7)) + facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  xlab("") + ylab("Signature") + 
  theme(plot.margin=unit(c(0,0,0,0), unit="cm"))
@
\caption{\label{fig:aligned}Overview of aligned signatures for all bullet lands for the ten barrels of the Hamby study. }
\end{figure}

@@

\begin{table}[tbhp]
\caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
\centering
<<importance, echo=FALSE, results='asis', warning=FALSE>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp <- imp[order(-imp$MeanDecreaseGini),]
names(imp)[1] <- "Importance"
imp <- imp[,2:1]
imp$meanMatch <- sapply(imp$Variable, function(var) {
  mean(subset(bstats, match)[,var])
})
imp$sdMatch <- sapply(imp$Variable, function(var) {
  sd(subset(bstats, match)[,var])
})
imp$meanNonMatch <- sapply(imp$Variable, function(var) {
  mean(subset(bstats, !match)[,var])
})
imp$sdNonMatch <- sapply(imp$Variable, function(var) {
  sd(subset(bstats, !match)[,var])
})
imp$meanMatch <- round(imp$meanMatch,1)
imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
imp$meanNonMatch <- round(imp$meanNonMatch,1)
imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
row.names(imp) <- 1:nrow(imp)
imp$Variable[c(2,4)] <- c("#matches", "#non-matches")
names(imp)[-(1:2)] <- c("KM", "(sd)", "KNM", "(sd)")
print(xtable(imp, align="clrrd{3.2}rd{3.2}", digits=c(0,0,1,1,2,1,2)), 
      floating = FALSE)
@
\end{table}

>>>>

\section{Signature intensities}\label{supp:bulletbottom}
<<setup-signatures, echo=FALSE>>=
library(x3pr)
library(x3prplus)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(zoo)

@@

aligned <- crossSmooth %>% group_by(id) %>% do(
  data.frame(alignme(.))
)
aligned$land <- (aligned$id %% 6)
aligned$land[aligned$land==0] <- 6
aligned$bulletland <- aligned$bullet
aligned$bullet <- gsub("-[0-9]","",aligned$bullet)
library(RColorBrewer)
cols <- rep(brewer.pal(n=10, name="Paired"), length=35)[sample(35, 35, replace=TRUE)]
labels <- aligned %>% group_by(bulletland) %>% summarize(
  x = max(y),
  y = min(l30, na.rm=T),
  label = bullet[1],
  barrel = barrel[1],
  land = land[1]
)

qplot(x=y, y=l30, data=aligned, geom="line", group=bullet, colour=bullet) + 
  ylim(c(-7,7)) + xlab("") + ylab("Signature") + 
  facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  theme(plot.margin=unit(c(0,0,0,0), unit="cm"), legend.position="none") + 
  scale_colour_manual(values=cols) +
  geom_label(aes(x=x, y=y, label=label), data=labels, 
             inherit.aes = FALSE)
@
\caption{\label{fig:aligned}Overview of aligned signatures for all bullet lands for the ten barrels of the Hamby study. }
\end{figure}

@@

\begin{table}[tbhp]
\caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
\centering
<<importance, echo=FALSE, results='asis', warning=FALSE>>=
imp <- data.frame(importance(rtrees2))
imp$Variable <- row.names(imp)

imp2 <- data.frame(importance(rtrees3))
imp2$Variable <- row.names(imp2)
names(imp2)[1] <- "Bigforest"
imp <- merge(imp, imp2, by="Variable")

imp <- imp[order(-imp$MeanDecreaseGini),]
names(imp)[2:3] <- c("Importance 1", "Importance 2")

bstats <- subset(ballstats, insmall == TRUE)
imp$meanMatch <- sapply(imp$Variable, function(var) {
  mean(subset(bstats, match)[,var])
})
imp$sdMatch <- sapply(imp$Variable, function(var) {
  sd(subset(bstats, match)[,var])
})
imp$meanNonMatch <- sapply(imp$Variable, function(var) {
  mean(subset(bstats, !match)[,var])
})
imp$sdNonMatch <- sapply(imp$Variable, function(var) {
  sd(subset(bstats, !match)[,var])
})

imp$meanMatch <- round(imp$meanMatch,1)
imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
imp$meanNonMatch <- round(imp$meanNonMatch,1)
imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
row.names(imp) <- 1:nrow(imp)
imp$Variable[c(2,3,4,6,8)] <- c("#matches", "S", "#non-matches", "CMS", "CNMS")
names(imp)[-(1:3)] <- c("KM", "(sd)", "KNM", "(sd)")
print(xtable(imp, align="clrrrd{3.2}rd{3.2}", digits=c(0,0,1,1,1,2,1,2)), 
      floating = FALSE)
@
\end{table}
